---
title: "Time Series Project"
author:
  - Greg Lazenby
  - Rebecca Holsapple
date: April 11, 2020
output: html_notebook
---


Source data:
https://transtats.bts.gov/dl_selectfields.asp?table_id=236

For this example I used the site above and downloaded data using the following selections:

- Filter Geography = All
- Filter Year = 2019
- Filter Period = January

- Time Period = FlightDate
- Airline = Reporting_Airline
- Origin = OriginAirportID
- Destination = DestAirportID
- Departure Performance = DepDelay
- Arrival Performance = ArrDelay
- Cancellations and Diversions = Cancelled
- Flight Summaries = Flights
- Cause of Delay = CarrierDelay

```{r}
library(tswge)
flight = read.csv("29496285_T_ONTIME_REPORTING.csv")
```


This results in data with 583,985 observations with 9 variables. Actually there are 10 variables because a variable called "X" was included but I'm not sure what this is?

However, it's clear we need to narrow down some things. Maybe to a specific airline and location and possibly pick something like departure delay to predict. For instance, here I've filtered to a single carrier and DFW as the origin airport. 

```{r}
# data filtered to AA departure delay at location 11298 (DFW Airport)
aa.dep.delay = subset(flight, (OP_UNIQUE_CARRIER == "AA" & ORIGIN_AIRPORT_ID == 11298), select = c("DEP_DELAY"))
```

Looking at the plots below there doesn't seem to be too much structure in the realization. It pretty much looks like white noise, but then again this is just a single month. 

```{r}
invisible(
  plotts.sample.wge(na.omit(aa.dep.delay$DEP_DELAY))
)
```


